### 2023-04-29 figures/N3_CLVR_cycle.tex
Peter's fixes 4/28

\begin{tikzpicture}[node distance = 2cm, auto]
    % Create elements
    % \node [element] (fc) {Flight Conditions};
    \node [element] (inlet) {Inlet};
    \node [element, right=4em of inlet] (fan) {Fan};
    \node [element, right=4em of fan] (splitter) {Splitter};
    \node [element, right=4em of splitter] (lpc) {Low Pressure Compressor};
    \node [element, right=4em of lpc ] (injector) {Water Injector};
    \node [element, right=4em of injector ] (hpc) {High Pressure Compressor};
    \node [element, right=4em of hpc] (burner) {Burner};
    \node [element, right=4em of burner] (hpt) {High-Pressure Turbine};
    \node [element, right=4em of hpt] (lpt) {Low-Pressure Turbine};
    \node [element, right=4em of lpt] (extractor) {Water Extractor};
    \node [element, right=4em of extractor] (corenozzle) {Core Nozzle};
    \node [element, below=4em of burner] (vrl) {Vapor Recovery Loop};
    \node [element, below=12em of burner] (bypduct) {Bypass Duct};
    \node [element, below=12em of corenozzle] (bypnozzle) {Bypass Nozzle};

    % Add shaft elements
    \node [shaft_element, above=8em of $(hpc)!0.5!(hpt)$] (hpshaft) {High Pressure Shaft};
    \node [shaft_element, above=16em of $(lpc)!0.5!(lpt)$] (lpshaft) {Low Pressure Shaft};
    \node [shaft_element, above=16em of $(fan)!0.28!(lpc)$] (fanshaft) {Fan Shaft};
    \node [shaft_element, above=16em of $(fan)!0.72!(lpc)$] (gearbox) {Gearbox};

    % Draw element connections
    % \path [connection] (fc) -- (inlet);
    \path [connection] (inlet) -- (fan);
    \path [connection] (fan) -- (splitter);
    \path [connection] (splitter) -- (lpc);
    \path [connection] (splitter) |- (bypduct);
    \path [connection] (bypduct) -- (bypnozzle);
    \path [connection] (lpc) -- (injector);
    \path [connection] (injector) -- (hpc);
    \path [connection] (hpc) -- (burner);
    \path [connection] (burner) -- (hpt);
    \path [connection] (hpt) -- (lpt);
    \path [connection] (lpt) -- (extractor);
    \path [connection] (extractor) -- (corenozzle);
    \path [connection] (extractor) |- (vrl);
    \path [connection] (vrl) -| (injector);

    % Draw Shaft Connections
    \path [shaft] (fan) |- (fanshaft) -- (gearbox);
    \path [shaft] (gearbox) -| (lpc);
    \path [shaft] (lpc) |- (lpshaft) -| (lpt);
    \path [shaft] (hpc) |- (hpshaft) -| (hpt);

>>>>

\begin{tikzpicture}[node distance = 2cm, auto]
    % Create elements
    % \node [element] (fc) {Flight Conditions};
    % \node [element] (inlet) {Inlet};
    % \node [element, right=4em of inlet] (fan) {Fan};
    % \node [element, right=4em of fan] (splitter) {Splitter};
    \node [element] (lpc) {Low Pressure Compressor};
    \node [element, right=4em of lpc ] (injector) {Water Injector};
    \node [element, right=4em of injector ] (hpc) {High Pressure Compressor};
    \node [element, right=4em of hpc] (burner) {Burner};
    \node [element, right=4em of burner] (hpt) {High-Pressure Turbine};
    \node [element, right=4em of hpt] (lpt) {Low-Pressure Turbine};
    \node [element, right=4em of lpt] (extractor) {Water Extractor};
    \node [element, right=4em of extractor] (corenozzle) {Core Nozzle};
    \node [element, below=4em of burner] (vrl) {Vapor Recovery Loop};
    % \node [element, below=12em of burner] (bypduct) {Bypass Duct};
    % \node [element, below=12em of corenozzle] (bypnozzle) {Bypass Nozzle};

    % Add shaft elements
    % \node [shaft_element, above=8em of $(hpc)!0.5!(hpt)$] (hpshaft) {High Pressure Shaft};
    % \node [shaft_element, above=16em of $(lpc)!0.5!(lpt)$] (lpshaft) {Low Pressure Shaft};
    % \node [shaft_element, above=16em of $(fan)!0.28!(lpc)$] (fanshaft) {Fan Shaft};
    % \node [shaft_element, above=16em of $(fan)!0.72!(lpc)$] (gearbox) {Gearbox};

    % Draw element connections
    % \path [connection] (fc) -- (inlet);
    % \path [connection] (inlet) -- (fan);
    % \path [connection] (fan) -- (splitter);
    % \path [connection] (splitter) -- (lpc);
    % \path [connection] (splitter) |- (bypduct);
    % \path [connection] (bypduct) -- (bypnozzle);
    \path [connection] (lpc) -- (injector);
    \path [connection] (injector) -- (hpc);
    \path [connection] (hpc) -- (burner);
    \path [connection] (burner) -- (hpt);
    \path [connection] (hpt) -- (lpt);
    \path [connection] (lpt) -- (extractor);
    \path [connection] (extractor) -- (corenozzle);
    \path [connection] (extractor) |- (vrl);
    \path [connection] (vrl) -| (injector);

    % Draw Shaft Connections
    % \path [shaft] (fan) |- (fanshaft) -- (gearbox);
    % \path [shaft] (gearbox) -| (lpc);
    % \path [shaft] (lpc) |- (lpshaft) -| (lpt);
    % \path [shaft] (hpc) |- (hpshaft) -| (hpt);
